Magnetic inhibition of convection and the fundamental properties of low--mass stars

### 2016-07-13 paper/ms.tex
integrated new commands from defs

\usepackage{defs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

While other young stellar populations exhibit an age gradient as a function of effective temperature, Upper Scorpius poses a particularly interesting hurdle. Previous studies of this problem are confined to the theoretical HR diagram and suffer from significant uncertainties in the accuracy of inferred stellar properties. However, observations of Upper Scorpius by \emph{Kepler}/K2 during Campaign 2 provide accurate photometric lightcurves of eclipsing multi-star systems \citep{Kraus2015, Alonso2015, David2016, Lodieu2015}. This opens up new territory for assessing hypotheses as to the origin of the noted age discordance. Models can now be constrained in the HR diagram with added constraints from the eclipsing binary mass-radius relationship. The empirical mass-radius relationship is more reliable than the HR diagram, as masses and radii can be measured directly \citep[e.g.,][]{Andersen1991,Torres2010}. Compare this to conversions from spectral types and photometric colors to \teff s and luminosities, which are subject to significant uncertainties, especially for stars with gravities intermediate between dwarf and giant scales \citep[see, e.g.,][]{Pecaut2013}. Empirical mass-radius relationships should therefore provide stringent tests of stellar model accuracy.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\msun}{$M_{\odot}$}
\newcommand{\rsun}{$R_{\odot}$}
\newcommand{\lsun}{$L_{\odot}$}
\newcommand{\logLsun}{\log(L/L_{\odot})}
\newcommand{\amlt}{\alpha_{\rm MLT}}
\newcommand{\teff}{$T_{\rm eff}$}
\newcommand{\tauf}{\tau_{\rm fit}}
\newcommand{\lbol}{$L_{\rm bol}$}
\newcommand{\fbol}{$F_{\rm bol}$}
\newcommand{\logg}{$\log g$}
\newcommand{\vsini}{$v \sin i$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\lha}{$L_{\rm H\alpha}$}
\newcommand{\water}{H$_2$O}
\newcommand{\pgas}{P_{\rm gas}}
\newcommand{\porb}{$P_{\rm orb}$}

@@

While other young stellar populations exhibit an age gradient as a function of effective temperature, Upper Scorpius poses a particularly interesting hurdle. Previous studies of this problem are confined to the theoretical HR diagram and suffer from significant uncertainties in the accuracy of inferred stellar properties. However, observations of Upper Scorpius by \emph{Kepler}/K2 during Campaign 2 provide accurate photometric lightcurves of eclipsing multi-star systems \citep{Kraus2015, Alonso2015, David2016, Lodieu2015}. This opens up new territory for assessing hypotheses as to the origin of the noted age discordance. Models can now be constrained in the HR diagram with added constraints from the eclipsing binary mass-radius relationship. The empirical mass-radius relationship is more reliable than the HR diagram, as masses and radii can be measured directly \citep[e.g.,][]{Andersen1991,Torres2010}. Compare this to conversions from spectral types and photometric colors to $T_{\rm eff}$s and luminosities, which are subject to significant uncertainties, especially for stars with gravities intermediate between dwarf and giant scales \citep[see, e.g.,][]{Pecaut2013}. Empirical mass-radius relationships should therefore provide stringent tests of stellar model accuracy.
